%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Extracurricular Activity}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Core Member} % Affiliation/role
    {Game Development Team - Northwestern IEEE} % Organization/group
    {Evanston, IL} % Location
    {Jan. 2018 - Mar. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Gained expertise in unit testing areas, especially targeted on desktop application and software.}
        \item {Built applications in Unity with guidance and pair programming with a senior software developer.}
        \item {Contributed heavily in implementing level generation and NPC interaction in 2017-2018 IEEE's game development project (Do Not Touch the Ground).}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Participant} % Affiliation/role
    {Grow with Google Challenge Scholarship: Mobile Web} % Organization/group
    {Online - Udacity} % Location
    {Jan. 2018 - Mar. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Identified the benefits offline-first bring to standard web apps and its impact on user experience.}
        \item {Obtained knowledge of the service worker and indexDB in regards to the request response cycle when connection fails.}
        \item {Implemented caching for a basic news feed app using the service worker and indexDB to improve user experience when the connection is offline, lie-fi, or slow such that the app would load previously old content  stored in the local cache until the user is able to connect online.}
      \end{cvitems}
    }

\end{cventries}